Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-16 Draft/contributions.tex
some improvements in the draft
Updated contributions section

At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$.
In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are reported.
The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
The QCD contribution does not posses external gluons due to charge conservation.
Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchange in the $t/u$-channel between the quark lines.
This results in a small contribution although the VBS cuts have not been imposed.
The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top), $\mathcal{O}(\alphas\alpha^5)$ (middle), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
\MP{On the plots: it should be $\alpha$ and not $\alpha_{em}$ and $m_{\Pj\Pj}$ instead of $M_{jj}$. And we have the convention to put $\alphas$ before $\alpha$.}}
\label{fig:mjjdyjj_2d_LO}
\end{figure}

>>>>

At tree level, there are three contributions to the $\PW^+\PW^+$ production in association with two jets: the pure EW component $\mathcal{O}(\alpha^6)$, the interference $\mathcal{O}(\alphas\alpha^5)$, and the QCD background $\mathcal{O}(\alphas^2\alpha^4)$ \AK{We have mentioned this many times at this point. Perhaps not worth repeating again?}.
In the present section, the cross sections and distributions are obtained without applying the VBS cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$.
In Tab.~\ref{tab:LOscanXsec}, the cross sections of the three contributions are reported.
The EW, QCD, and interference contributions amount to $57\%$, $37\%$, and $6\%$ of the total inclusive cross section, respectively.
The QCD contribution does not posses external gluons due to charge conservation.
Thus the $\mathcal{O}(\alphas^2\alpha^4)$ diagrams only involve gluon exchange in the $t/u$-channel between the quark lines.
This results in a small contribution although the VBS cuts have not been imposed.
The interference between EW and QCD contributions is small, due to color suppression, but not negligible ($t/u$ interference with identical fermions).

@@

\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew6.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew5qcd1.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/scan_ew4qcd2.pdf}
\caption{Cross sections (fb) per bin in the plan $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ for the three LO contributions of orders $\mathcal{O}(\alpha^6)$ (top), $\mathcal{O}(\alphas\alpha^5)$ (middle), and $\mathcal{O}(\alphas^2 \alpha^4)$ (bottom).
\MP{On the plots: it should be $\alpha$ and not $\alpha_{em}$ and $m_{\Pj\Pj}$ instead of $M_{jj}$. And we have the convention to put $\alphas$ before $\alpha$.}}
\label{fig:mjjdyjj_2d_LO}
\end{figure*}
